---
title: "Still suspicious: The suspicious coincidence effect revisited"
subtitle: Supplementary Information
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: false
    theme: cerulean
    toc_float: true
    toc: true
    code_folding: hide
---
  
******
******


```{r setup, include = F}
rm(list = ls())

# load packages
library(knitr)
library(rmarkdown)
library(broom)
library(tidyverse) 
library(langcog)
library(forcats)
library(compute.es)
library(stringr)
library(metafor)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, cache = T, tidy = F, fig.height = 4)
```  

```{r read_in_anon_data}
files <- dir("../../data/munged_data/")[-1]
all_d <- data.frame()
for (i in 1:length(files)[1]) {
    s <- read_csv(paste0("../../data/munged_data/", files[i]))
    all_d <- bind_rows(all_d, data.frame(s))
}

exp_key <- read_csv("../../analysis/experiment_key.csv") %>%
              mutate(order = gsub("\"", "", order))
```


##  Effect size by category 
The plot below shows the effect size for each experiment (facet) for each of the three categories in our stimuli (animals, vegetables and vehicles). While there is some variability in effect size by category (the effect larger for animals), this variability is small relative to the effect of condition order. For reference, Table 1 describes the characteristics of each of the experiments.

```{r get_means}
# remap condition values and select relevant conditions
all_d_clean <- all_d %>%
      mutate(condition = as.factor(condition),
             exp = as.character(exp),
             condition = fct_recode(condition,
                                     three_basic = "3bas",
                                     three_subordinate = "3sub",
                                     three_superordinate = "3sup")) %>%
      filter(condition == "one" | condition == "three_subordinate") %>%
      select(exp, everything())

all_ms_subj <- all_d_clean %>%
  left_join(exp_key %>% select(exp, exp_recoded)) %>%
  select(-exp) %>%
  gather(variable, value, c(prop_sub, prop_bas, prop_sup)) %>%
  group_by(condition, category, variable, exp_recoded, subids) %>%
  mutate(value = as.numeric(value)) %>%
  summarize(value = mean(value)) %>%
  filter(condition == "one" | condition == "three_subordinate",
         variable == 'prop_bas') %>%
  spread(condition, value) %>%
  ungroup() %>%
  select(-variable)

LF_means <- all_ms_subj %>%
  group_by(exp_recoded, category) %>%
  summarize(m_one = mean(one),
            sd_one = sd(one),
            m_3sub = mean(three_subordinate),
            sd_3sub = sd(three_subordinate),
            n = n())

LF_effect_sizes <- LF_means %>%
  ungroup() %>%
  do(data.frame(d = mes(.$m_one, .$m_3sub, .$sd_one,
                     .$sd_3sub, .$n, .$n, verbose = F)$d,
               d_var = mes(.$m_one, .$sd_3sub, .$sd_one,
                    .$sd_3sub, .$n, .$n, verbose = F)$var.d)) %>%
  mutate(high = d + (1.96*d_var),
         low = d - (1.96*d_var),
         es_type = "nonpaired",
         exp_recoded = LF_means$exp_recoded,
         category = LF_means$category) %>%
  left_join(LF_means %>% select(exp_recoded, n)) %>%
  select(exp_recoded, n, everything()) %>%
  mutate(exp_recoded = as.numeric(exp_recoded))
```

```{r, fig.height = 5, fig.width = 7}
ggplot(LF_effect_sizes, aes(x = category, 
                            color = category,
                            y = d)) +
  geom_pointrange(size = .2, 
                    aes(ymax = high, 
                      ymin = low, 
                      color = category)) +
  geom_hline(yintercept = 0, linetype = 2, color = "black") +
  facet_wrap(~exp_recoded) +
  ggtitle("Effect size by category") + 
  ylab("Cohen's d") +
  ggthemes::theme_few()  +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        strip.background = element_rect(fill = "grey"))
```


```{r}
exp_table <- exp_key %>%
  slice(1:12) %>%

  mutate(direct_replication_of_string = ifelse(is.na(direct_replication_of),
                                              "", direct_replication_of),
         timing = str_replace_all(timing, "sequential", "seq."),
         timing = str_replace_all(timing, "simultaneous", "simult."),
         one_3sub_label = str_replace_all(one_3sub_label, "different", "diff."),
         exp_recoded = as.numeric(exp_recoded)) %>%
  select(exp_recoded, timing, order, blocking, 
         one_3sub_label, direct_replication_of_string) %>%
  arrange(exp_recoded)

kable(exp_table)

```

## Repeat participants excluded
```{r}
all_d_filtered <- read_csv("../../data/munged_data/all_data_munged_A.csv")

n_unique <- all_d_filtered %>%
  distinct(exp, subids) %>%
  summarize(n = n())

n_total <- all_d %>%
  distinct(exp, subids) %>%
  summarize(n = n())
  
prop_duplicates <- round((n_total-n_unique)/n_total, 2) * 100
```
`r prop_duplicates`% of  all participants (N = `r n_total`) participated in more than one experiment. The data reported in the main text include all participants. Below we plot the effect sizes with participants who had already participanted in a prior experiment excluded (effect size estimates from XT and SPSS are also included for reference)./ The overall pattern looks the same as with all participants.

```{r, fig.height = 5, fig.width = 7}
all_d_clean <- all_d_filtered %>%
      mutate(condition = as.factor(condition),
             exp = as.character(exp),
             condition = fct_recode(condition,
                                     three_basic = "3bas",
                                     three_subordinate = "3sub",
                                     three_superordinate = "3sup")) %>%
      filter(condition == "one" | condition == "three_subordinate") %>%
      select(exp, everything())

all_ms_subj <- all_d_clean %>%
  left_join(exp_key %>% select(exp, exp_recoded)) %>%
  select(-exp) %>%
  gather(variable, value, c(prop_sub, prop_bas, prop_sup)) %>%
  group_by(condition,variable, exp_recoded, subids) %>%
  mutate(value = as.numeric(value)) %>%
  summarize(value = mean(value)) %>%
  filter(condition == "one" | condition == "three_subordinate", 
         variable == 'prop_bas') %>%
  spread(condition, value) %>%
  ungroup() %>%
  select(-variable)

# get effect sizes
LF_means <- all_ms_subj %>%
  group_by(exp_recoded) %>%
  summarize(m_one = mean(one),
            sd_one = sd(one),
            m_3sub = mean(three_subordinate),
            sd_3sub = sd(three_subordinate),
            n = n())

LF_effect_sizes <- LF_means %>%
  do(data.frame(d = mes(.$m_one, .$m_3sub, .$sd_one,
                     .$sd_3sub, .$n, .$n, verbose = F)$d,
               d_var = mes(.$m_one, .$sd_3sub, .$sd_one,
                    .$sd_3sub, .$n, .$n, verbose = F)$var.d)) %>%
  mutate(high = d + (1.96*d_var),
         low = d - (1.96*d_var),
         es_type = "nonpaired",
         exp_recoded = LF_means$exp_recoded) %>%
  left_join(LF_means %>% select(exp_recoded, n)) %>%
  select(exp_recoded, n, everything())

literature_effect_sizes <- read_csv("../../data/literature_ES.csv") # see ../analysis/get_literature_ES.R

all_es <- literature_effect_sizes %>%
           bind_rows(LF_effect_sizes) %>%
            left_join(exp_key) %>%
            mutate(source = ifelse(str_detect(exp_recoded, "XT"), "XT2007a", 
                               ifelse(str_detect(exp_recoded, "SPSS"), "SPSS2011", "LF")), 
                   source = fct_relevel(source, "XT2007a","SPSS2011","LF"),
                   timing = fct_relevel(timing,"simultaneous", "sequential")) %>%
            mutate(source = as.numeric(source))

seq13 <- rma(d, d_var, dat = filter(all_es, timing == "sequential", order == "1-3"))
seq31 <- rma(d, d_var, dat = filter(all_es, timing == "sequential", order == "3-1"))
sim13 <- rma(d, d_var, dat = filter(all_es, timing == "simultaneous", order == "1-3"))
sim31 <- rma(d, d_var, dat = filter(all_es, timing == "simultaneous", order == "3-1"))

ma_es <- data.frame(order = c("1-3", "3-1", "1-3", "3-1"),
           timing = c("sequential", "sequential", "simultaneous", "simultaneous"),
           d = c(seq13$b[[1]], seq31$b[[1]], sim13$b[[1]], sim31$b[[1]]),
           d_low = c(seq13$ci.lb[[1]], seq31$ci.lb[[1]], sim13$ci.lb[[1]], sim31$ci.lb[[1]]),
           d_high = c(seq13$ci.ub[[1]], seq31$ci.ub[[1]], sim13$ci.ub[[1]], sim31$ci.ub[[1]]))

ggplot(all_es) +
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = d_low, ymax = d_high), 
            fill = "red", alpha = 0.05, inherit.aes = FALSE, data = ma_es) +
  geom_hline(aes(yintercept = d), data = ma_es, color = "red") +
  scale_color_manual(values = c("black","grey63")) +
  geom_pointrange(aes(x = jitter(source, 1.4),  y = d, ymax = high, 
                      ymin = low, color = one_3sub_label, shape = fct_rev(blocking)), 
                  size = .5) +
  geom_hline(yintercept = 0, linetype = 2, color = "black") +
  facet_grid(order ~ timing) +
  scale_x_continuous(breaks = c(1:3), limits = c(.6, 3.3),
                     labels = c("XT","SPSS","LF")) +
  ylab("Cohen's d") +
  xlab("Paper") + 
  guides(color = guide_legend("Label"),
         shape = guide_legend("Blocking"))  +
  ggthemes::theme_few()

```

## Demographics
```{r}
raw_files <- dir("../../data/anonymized_raw_data/")
raw_d <- data.frame()
for (i in 1:length(raw_files)[1]) {
    s <- read_csv(paste0("../../data/anonymized_raw_data/", raw_files[i])) %>%
        mutate(exp = unlist(str_split(files[i], "_|exp"))[2]) %>%
        select(exp, subids, SubmitTime, AcceptTime,
               asses, comments, age, gender, education, enjoyment, language)
    raw_d <- bind_rows(raw_d, data.frame(s))
}

raw_d_munged <- raw_d %>%
  left_join(exp_key %>% select(exp, exp_recoded, timing)) %>%
  mutate(exp_recoded = fct_relevel(exp_recoded, "10", after = 9),
         exp_recoded = fct_relevel(exp_recoded, "11", after = 10)) %>%
  select(-exp) %>%
  ungroup()
```

### Education
```{r}
raw_d_munged %>%
  mutate(education = as.factor(education),
         education = fct_recode(education,
                        "No Response" = "-1",
                        "Some High School" = "0",
                        "Graduated High School" = "1",
                        "Some College"= "2",
                        "Graduated College" = "3",
                        "Hold a higher degree" = "4")) %>%
  group_by(education) %>%
  summarise(n = n()) %>%
  mutate(prop = round(n / sum(n),2)) %>%
  kable()
```

### First language
```{r}
raw_d_munged %>%
  mutate(language = tolower(language),
         language = ifelse(substr(language,0,1) == "e", # all e lanuages are english
                           "English", "Other")) %>%
  group_by(language) %>%
    summarise(n = n()) %>%
  mutate(prop = round(n / sum(n),2)) %>%
  kable()
```

### Gender
```{r}
raw_d_munged %>%
  group_by(gender) %>%
  summarise(n = n()) %>%
  mutate(prop = round(n / sum(n),2)) %>%
  kable()
```

### Age
```{r}

raw_d_munged %>%
  mutate(age = as.numeric(as.character(age))) %>%
  ggplot(aes(x = age)) +
  geom_histogram() +
  geom_vline(aes(xintercept = mean(as.numeric(as.character(age)),
                                   na.rm = T)), 
                 color = "red") +
  xlab("Age (years)") +
  theme_bw() +
  ggtitle("Age distribution")
```

## Task feedback
```{r}
raw_d_munged %>%
  mutate(enjoyment = as.factor(enjoyment),
         enjoyment = fct_recode(enjoyment,
                        "No Response" = "-1",
                        "Worse than the Average HIT" = "0",
                        "An Average HIT" = "1",
                        "Better than average HIT" = "2")) %>%
  group_by(enjoyment) %>%
  summarise(n = n()) %>%
  mutate(prop = round(n / sum(n),2)) %>%
  kable()

raw_d_munged %>%
  mutate(asess = as.factor(asses)) %>%
  rename(`Did you read instructions?` = "asses") %>%
  group_by(`Did you read instructions?`) %>%
  summarise(n = n()) %>%
  mutate(prop = round(n / sum(n),2)) %>%
  kable()

#unique(raw_d_munged$comments)
```

## Task time
Task times were variable across experiments, but overall shorter for simultaneous timing experiments (green) compared to sequential (pink).
```{r}
# fix this - dplyr doesn't play well with dates
raw_d_mungedT <- raw_d_munged
raw_d_mungedT$SubmitTime = gsub("T|Z","",raw_d_mungedT$SubmitTime)
raw_d_mungedT$AcceptTime = gsub("T|Z","",raw_d_mungedT$AcceptTime)
raw_d_mungedT$SubmitTime = strptime(raw_d_munged$SubmitTime, "%F%T")
raw_d_mungedT$AcceptTime = strptime(raw_d_mungedT$AcceptTime, "%F%T")
raw_d_mungedT$total_time = as.numeric(raw_d_mungedT$SubmitTime) - as.numeric(raw_d_mungedT$AcceptTime)

ggplot(raw_d_mungedT, 
       aes(x = exp_recoded, y = total_time/60, fill = timing)) +
    ylab("Time (min.)") +
    xlab("Experiment") +
    ggtitle("Task time")+
    geom_boxplot() +
    ggthemes::theme_few()  
```

