---
title: XTMEM SI
subtitle: Meta-analysis of experiments
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: false
    theme: cerulean
    toc_float: true
    toc: true
    code_folding: show
---
  
******
******


```{r setup, include = F}
rm(list=ls())

# load packages
library(knitr)
library(rmarkdown)
library(broom)
library(tidyverse) 
library(langcog)
library(forcats)
library(compute.es)
library(stringr)


#source("useful_ML.R")

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, cache = F, tidy = F, fig.height = 4)
```  

Read in all previous anonymzed data and bind to current dataset
```{r read_in_anon_data}
files <- dir("../../data/munged_data/")
all_d <- data.frame()
for (i in 1:length(files)[1]) {
    s <- read_csv(paste0("../../data/munged_data/", files[i]))
    all_d <- bind_rows(all_d, data.frame(s))
}

exp_key <- read_csv("../../analysis/experiment_key.csv") %>%
              mutate(order = gsub("\"", "", order))# this is because excel is dumb, grrr
```


##  By category analysis
The plot shows the effect size for each experiment (each facet) for each of the three categories in our stimuli (animals, vegetables and vehicles). While there is some variability in effect size by category (the effect larger for animals), this variability is small relative to the effect of condition order.

```{r get_means}
# remap condition values and select relevant conditions
all_d_clean <- all_d %>%
      mutate(condition = as.factor(condition),
             exp = as.character(exp),
             condition = fct_recode(condition,
                                     three_basic = "3bas",
                                     three_subordinate = "3sub",
                                     three_superordinate = "3sup")) %>%
      filter(condition == "one" | condition == "three_subordinate") %>%
      select(exp, everything())

all_ms_subj <- all_d_clean %>%
  left_join(exp_key %>% select(exp, exp_recoded)) %>%
  select(-exp) %>%
  gather(variable, value, c(prop_sub, prop_bas, prop_sup)) %>%
  group_by(condition, category, variable, exp_recoded, subids) %>%
  mutate(value = as.numeric(value)) %>%
  summarize(value = mean(value)) %>%
  filter(condition == "one" | condition == "three_subordinate",
         variable == 'prop_bas') %>%
  spread(condition, value) %>%
  ungroup() %>%
  select(-variable)

LF_means <- all_ms_subj %>%
  group_by(exp_recoded, category) %>%
  summarize(m_one = mean(one),
            sd_one = sd(one),
            m_3sub = mean(three_subordinate),
            sd_3sub = sd(three_subordinate),
            n = n())

LF_effect_sizes <- LF_means %>%
  ungroup() %>%
  do(data.frame(d = mes(.$m_one, .$m_3sub, .$sd_one,
                     .$sd_3sub, .$n, .$n, verbose = F)$d,
               d_var = mes(.$m_one, .$sd_3sub, .$sd_one,
                    .$sd_3sub, .$n, .$n, verbose = F)$var.d)) %>%
  mutate(high = d + (1.96*d_var),
         low = d - (1.96*d_var),
         es_type = "nonpaired",
         exp_recoded = LF_means$exp_recoded,
         category = LF_means$category) %>%
  left_join(LF_means %>% select(exp_recoded, n)) %>%
  select(exp_recoded, n, everything()) %>%
  mutate(exp_recoded = as.numeric(exp_recoded))
```

```{r}
ggplot(LF_effect_sizes, aes(x = category, 
                            color = category,
                            y = d)) +
  geom_pointrange(size = .2, 
                    aes(ymax = high, 
                      ymin = low, 
                      color = category)) +
  geom_hline(yintercept = 0, linetype = 2, color = "black") +
  facet_wrap(~exp_recoded) +
  ggtitle("Effect size by category")+ 
  ylab("Cohen's d") +
  ggthemes::theme_few()  +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        strip.background = element_rect(fill = "grey"))
```

### Duplicates
TO DO: look at ES excluide duplicates (about 10%)
```{r, include = F,  eval = F}
NUMEXPS <- 8

d = data.frame()
for (j in 1:NUMEXPS){
  files = dir(paste0("../experiments/exp", as.character(j), "/production-results/"))
  for (i in 1:length(files)[1]) {
      s <- fromJSON(paste0("../experiments/exp", as.character(j), "/production-results/", files[i]))
      s$exp = j
      s$answers$asses = ifelse(is.null(s$answers$asses), "NA", s$answers$asses)
      d = bind_rows(d, data.frame(s))
  }
}
names(d) <- str_replace(names(d), "answers.", "")

d$WorkerId = as.factor(d$WorkerId)

hit.counts = group_by(d, WorkerId) %>%
  summarize(count = n()) %>%
  arrange(-count) %>%
  filter(count > 1) %>%
  left_join(select(d, WorkerId, exp))

good.hits = hit.counts %>%
  group_by(WorkerId) %>%
  mutate(first_exp = min(exp),
         include = as.factor(ifelse(exp == first_exp, "keep", "remove"))) 
```



## Task time
Task times were quite variable but shorter for simultaneous timing experiments (green) compared to sequential (pink).
```{r}
raw_files <- dir("../../data/anonymized_raw_data/")
raw_d <- data.frame()
for (i in 1:length(raw_files)[1]) {
    s <- read_csv(paste0("../../data/anonymized_raw_data/", raw_files[i])) %>%
        mutate(exp = unlist(str_split(files[i], "_|exp"))[2]) %>%
        select(exp, subids, SubmitTime, AcceptTime,
               asses, comments, age, gender, education, enjoyment, language)
    raw_d <- bind_rows(raw_d, data.frame(s))
}

raw_d_munged <- raw_d %>%
  left_join(exp_key %>% select(exp, exp_recoded, timing)) %>%
  mutate(exp_recoded = fct_relevel(exp_recoded, "10", after = 9),
         exp_recoded = fct_relevel(exp_recoded, "11", after = 10)) %>%
  select(-exp) %>%
  ungroup()

# fix this - dplyr doesn't play well with dates
raw_d_mungedT <- raw_d_munged
raw_d_mungedT$SubmitTime = gsub("T|Z","",raw_d_mungedT$SubmitTime)
raw_d_mungedT$AcceptTime = gsub("T|Z","",raw_d_mungedT$AcceptTime)
raw_d_mungedT$SubmitTime = strptime(raw_d_munged$SubmitTime, "%F%T")
raw_d_mungedT$AcceptTime = strptime(raw_d_mungedT$AcceptTime, "%F%T")
raw_d_mungedT$total_time = as.numeric(raw_d_mungedT$SubmitTime) - as.numeric(raw_d_mungedT$AcceptTime)

ggplot(raw_d_mungedT, 
       aes(x = exp_recoded, y = total_time/60, fill = timing)) +
    ylab("raw_d_munged time (min.)") +
    xlab("Experiment Num.") +
    ggtitle("Task time")+
    geom_boxplot() +
    ggthemes::theme_few()  
```

### Demographics
```{r}
raw_d_munged %>%
  mutate(education = as.factor(education),
         education = fct_recode(education,
                        "No Response" = "-1",
                        "Some High School" = "0",
                        "Graduated High School" = "1",
                        "Some College"= "2",
                        "Graduated College" = "3",
                        "Hold a higher degree" = "4")) %>%
  group_by(education) %>%
  summarise(n = n()) %>%
  mutate(prop = round(n / sum(n),2)) %>%
  kable()

raw_d_munged %>%
  mutate(language = tolower(language)) %>%
  group_by(language) %>%
  summarise(n = n()) %>%
  kable()

raw_d_munged %>%
  group_by(gender) %>%
  summarise(n = n()) %>%
  mutate(prop = round(n / sum(n),2)) %>%
  kable()

raw_d_munged %>%
  mutate(age = as.numeric(as.character(age))) %>%
  ggplot(aes(x = age)) +
  geom_histogram() +
  geom_vline(aes(xintercept = mean(as.numeric(as.character(age)),
                                   na.rm = T)), 
                 color = "red") +
  xlab("Age (years)") +
  theme_bw() +
  ggtitle("Age distribution")
```

Task questions
```{r}
raw_d_munged %>%
  mutate(enjoyment = as.factor(enjoyment),
         enjoyment = fct_recode(enjoyment,
                        "No Response" = "-1",
                        "Worse than the Average HIT" = "0",
                        "An Average HIT" = "1",
                        "Better than average HIT" = "2")) %>%
  group_by(enjoyment) %>%
  summarise(n = n()) %>%
  mutate(prop = round(n / sum(n),2)) %>%
  kable()

raw_d_munged %>%
  mutate(asess = as.factor(asses)) %>%
  rename(`Did you read instructions?` = "asses") %>%
  group_by(`Did you read instructions?`) %>%
  summarise(n = n()) %>%
  mutate(prop = round(n / sum(n),2)) %>%
  kable()

#unique(raw_d_munged$comments)
```



