---
title: XTMEM4
subtitle: SPSS replication with blocking and diff labels
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: false
    theme: cerulean
    toc_float: true
    toc: true
    code_folding: show
---
  
******
******

Replication of SPSS 2011 with 2 methodological modifications from exp 2 (following SPSS): Blocking and reordering of trials (sub first), and using different label for all 12 trials. 

```{r setup, include = F}
rm(list=ls())

# load packages
library(knitr)
library(rmarkdown)
library(broom)
library(tidyverse) 
library(langcog)
library(jsonlite)
library(stringr)
library(png)
library(grid)
library(forcats)
library(effsize)
library(compute.es)

source("../../../analysis/useful_ML.R")


opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, cache = F, tidy = F, fig.height = 4)

```  

## Read in and process data
```{r, constants}
EXPTNUM <- 4
a.data.filename <- paste0("exp", EXPTNUM, "_A.csv")
```

```{r, eval = F}
files = dir("../production-results/")
d = data.frame()
for (i in 1:length(files)[1]) {
    s <- fromJSON(paste("../production-results/", files[i], sep = ""))
    s$answers$asses = ifelse(is.null(s$answers$asses), "NA", s$answers$asses)
    d = bind_rows(d, data.frame(s))
}
names(d) <- str_replace(names(d), "answers.", "")
d.anonymized <- anonymize.sids(d, "WorkerId")

#write.csv(d.anonymized, a.data.filename)
```

Munge
```{r}
d4 = read.csv(a.data.filename)

d4.long = d4 %>%
  gather(variable, value, contains("_")) %>%
  mutate(trial_num =  unlist(lapply(strsplit(as.character(variable),
                                      "_T"),function(x) x[2])),
         variable = unlist(lapply(strsplit(as.character(variable),
                                      "_"),function(x) x[1]))) %>%
  spread(variable, value) %>%
  mutate(trial_num = as.numeric(trial_num)) %>%
  mutate_if(is.character, funs(as.factor)) 

d4.munged = d4.long %>%
          select(subids, trial_num, category, condition, selected) %>%
          mutate(selected = lapply(str_split(selected, ","), 
                                   function(x) {str_sub(x, 4, 6)})) %>%
          mutate(prop_sub = unlist(lapply(selected, function(x){sum(x == "sub")/2})),
                 prop_bas = unlist(lapply(selected, function(x){sum(x == "bas")/2})),
                 prop_sup = unlist(lapply(selected, function(x){sum(x == "sup")/4}))) %>%
          select(-selected)
```

```{r, eval = F}
d4.munged$exp = EXPTNUM
#write.csv(d4.munged, paste0("../../../data/exp", EXPTNUM, "_data_munged.csv"), row.names = F)
```

## Reproduce XT2007a Fig. 5
```{r, fig.width = 8}
ms4 = d4.munged %>%
  gather(variable, value, c(prop_sub, prop_bas, prop_sup)) %>%
  group_by(condition,variable, subids) %>%
  mutate(value = as.numeric(value)) %>%
  summarize(value = mean(value)) %>%
  group_by(condition,variable) %>%
  multi_boot_standard(column = "value")  %>%
  mutate(variable = as.factor(variable))

ms.plot <- ms4
ms.plot$variable = factor(ms.plot$variable,levels(ms.plot$variable)[c(2,1,3)])
ms.plot$condition = factor(ms.plot$condition,levels(ms.plot$condition)[c(4,2,1,3)])
ms.plot$condition = plyr::mapvalues(ms.plot$condition,
                               from = c("one", "3bas", "3sub",
                                        "3sup"), 
                               to = c("1", "3 basic", "3 sub.", "3 super."))

ggplot(ms.plot, aes(x = condition, y = mean, group = variable, fill = variable)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, 
                     ymax = ci_upper), 
                 position=position_dodge(width = .9)) +
  ylab("Proportion of \ntest objects chosen") +
  xlab("Examples") +
  theme_bw() +
  theme(legend.title = element_blank())

```

## Reproduce SPSS Fig. 3
(plotting proportion basic level)

Read in all previous data and bind to current dataset
```{r}
files = dir("../../../data/")
all.d = data.frame()
for (i in 1:length(files)[1]) {
    s <- read.csv(paste0("../../../data/", files[i]))
    all.d = bind_rows(all.d, data.frame(s))
}
```

Get means and plot
```{r}
all.d$condition = plyr::mapvalues(all.d$condition,
                               from = c("one", "3bas", "3sub", "3sup"), 
                               to = c("one", "three_basic", 
                                        "three_subordinate",
                                        "three_superordinate"))
all.d$condition = as.factor(all.d$condition)

all.ms = all.d %>%
  gather(variable, value, c(prop_sub, prop_bas, prop_sup)) %>%
  group_by(condition,variable, exp, subids) %>%
  mutate(value = as.numeric(value)) %>%
  summarize(value = mean(value)) %>%
  group_by(condition,variable, exp) %>%
  multi_boot_standard(column = "value")  %>%
  ungroup() %>%
  mutate(variable = as.factor(variable)) %>%
  filter(condition == "one" | condition == "three_subordinate") %>%
  filter(variable == "prop_bas")

ggplot(all.ms, aes(x = exp, y = mean, group = condition, fill = condition)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, 
                     ymax = ci_upper), 
                 position=position_dodge(width = .9)) +
  ylim(0,1)+
  ylab("Proportion basic-level choices ") +
  xlab("Experiment") +
  theme_bw() +
  theme(legend.title = element_blank())
```

## Plot effect size

Get effect sizes of our experiments. Note that since we have the raw data available we can calculate the effect size taking into account the paired nature of the data, using effsize::cohen.d(paired = TRUE)).
```{r}
all.ms.subj = all.d %>%
  gather(variable, value, c(prop_sub, prop_bas, prop_sup)) %>%
  group_by(condition,variable, exp, subids) %>%
  mutate(value = as.numeric(value)) %>%
  summarize(value = mean(value)) %>%
  filter(condition == "one" | condition == "three_subordinate", variable == 'prop_bas') %>%
  spread(condition, value) %>%
  ungroup () %>%
  select(-variable)

conf.ints = all.ms.subj %>%
  group_by(exp) %>%
  do(data.frame(conf.int = effsize::cohen.d(.$one, .$three_subordinate, paired = T)$conf.int))  %>%
  ungroup() %>%
  mutate(bound=rep(c("low", "high"), 
                   length.out = EXPTNUM*2)) %>%
  spread(bound, conf.int) 

effect.sizes.paired = all.ms.subj %>%
  group_by(exp) %>%
  do(data.frame(d = effsize::cohen.d(.$one, .$three_subordinate, paired = T)$estimate)) %>%
  left_join(conf.ints) %>%
  ungroup () %>%
  mutate(es.type = "paired",
         exp = as.numeric(exp))

effect.sizes.npaired  = all.ms.subj %>%
  group_by(exp) %>%
  summarize(m.one = mean(one),
            sd.one = sd(one),
            m.3sub = mean(three_subordinate),
            sd.3sub = sd(three_subordinate),
            n= n()) %>%
  do(data.frame(d = mes(.$m.one, .$m.3sub, .$sd.one,
       .$sd.3sub, .$n, .$n, verbose = F)$d,
       var.d = mes(.$m.one, .$m.3sub, .$sd.one,
       .$sd.3sub, .$n, .$n, verbose = F)$var.d))%>%
  mutate(high = d + (1.96*var.d),
         low = d - (1.96*var.d),
         es.type = "nonpaired",
         exp = c(1:4))  # fix this

effect.sizes = bind_rows(effect.sizes.paired,
                         effect.sizes.npaired) %>%
  mutate(exp = as.factor(exp),
         n = 50) # fix this %>%

# make experiment nums meaningful
effect.sizes$exp = plyr::mapvalues(effect.sizes$exp ,
                               from = c("1", "2", "3", "4"), 
                               to = c("E1 XTa replication", "E2 SPSS replication", 
                                      "E3 XTa replication, blocked/diff labels", 
                                      "E4 SPSS replication, blocked/diff labels"))
```

Calculate effect sizes from previous experiments. Here are the means and sd based on SPSS table 1.
```{r}
original.effect.sizes = data.frame(exp = c("XT_adults_e1", "XT_children_e2",
                        "SPSS_e1",
                        "SPSS_e2",
                        "SPSS_e3",
                        "SPSS_eS1",
                        "SPSS_eS2"),
                        one_means = c(76, 40, 48.24, 30.83, 39.91, 24.56, 15.79), 
                        three_means = c(9, 6, 10.53, 53.33, 51.75, 16.67, 11.40),
                        one_sd = c(40.40, 40.40, 40.40,37.18,35.20,32.09,24.51),
                        three_sd = c(24.97, 24.97, 24.97,36.11,42.63,25.45,24.25),
                        n = c(22, 36, 19, 20, 19,19,19))
kable(original.effect.sizes)
```

Calculate previous effect sizes
```{r}
original.effect.sizes$d = mes(original.effect.sizes$one_means/100,
                              original.effect.sizes$three_means/100, 
                              original.effect.sizes$one_sd/100,
                              original.effect.sizes$three_sd/100,
                              original.effect.sizes$n,
                              original.effect.sizes$n, verbose = F)$d

original.effect.sizes$d_var = mes(original.effect.sizes$one_means/100,
                                  original.effect.sizes$three_means/100,
                                  original.effect.sizes$one_sd/100,
                                  original.effect.sizes$three_sd/100,
                                  original.effect.sizes$n, 
                                  original.effect.sizes$n,
                                  verbose = F)$var.d

original.effect.sizes = original.effect.sizes %>%
                            mutate(high = d + (1.96*d_var),
                                     low = d - (1.96*d_var)) %>%
                            select(-one_means, -three_means, -one_sd, -three_sd) %>%
                            mutate(es.type = "nonpaired")
```

Bind previous and current effect sizes together and plot
```{r, fig.height = 6}
all.es = bind_rows(original.effect.sizes, effect.sizes)
all.es$design <- c("simult.","simult.","simult.", "seq.", "seq.", "simult.", "simult.", "simult.", "seq.", "simult.", "seq." ,"simult.", "seq.", "simult.", "seq." )

ggplot(all.es, aes(x = exp, y = d, color = es.type)) +
  geom_point(aes(size = n))+
  geom_linerange(aes(ymax =high, ymin=low),
                 position = position_dodge(width = 0)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(design~., drop = TRUE, scales = "free_y")+
  coord_flip() +
  geom_hline(yintercept = 0, linetype = 2) +
  ggtitle("Effect size") +
  xlab("Experiment")
```

## Misc
### By category
```{r, fig.width = 9, fig.height = 3}
ms4 = d4.munged %>%
  gather(variable, value, c(prop_sub, prop_bas, prop_sup)) %>%
  mutate(variable = as.factor(variable)) %>%
  group_by(condition,variable, category, subids) %>%
  mutate(value = as.numeric(value)) %>%
  summarize(value = mean(value))%>%
  group_by(condition,variable,category) %>%
  multi_boot_standard(column = "value") 

ms4$variable = factor(ms4$variable,levels(ms4$variable)[c(2,1,3)])
ms4$condition = factor(ms4$condition,levels(ms4$condition)[c(4,2,1,3)])
ms4$condition = plyr::mapvalues(ms4$condition,
 from = c("one", "3bas", "3sub",
                                        "3sup"), 
                               to = c("1", "3 basic", "3 sub.", "3 super."))

ggplot(ms4, aes(x = condition, y = mean, group = variable, fill = variable)) +
  facet_grid(~category) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, 
                     ymax = ci_upper), 
                 position=position_dodge(width = .9)) +
  ylab("Proportion of \ntest objects chosen") +
  xlab("Examples") +
  theme_bw() +
  theme(legend.title = element_blank())
```

### Post-task questions
```{r}
d4 %>%
  group_by(education) %>%
  summarise(n = n()) %>%
  kable()

d4 %>%
  group_by(enjoyment) %>%
  summarise(n = n()) %>%
  kable()

d4 %>%
  mutate(language = tolower(language)) %>%
  group_by(language) %>%
  summarise(n = n()) %>%
  kable()

d4 %>%
  group_by(gender) %>%
  summarise(n = n()) %>%
  kable()

d4 %>%
  group_by(asses) %>%
  summarise(n = n()) %>%
  kable()

d4 %>%
  mutate(age = as.numeric(as.character(age))) %>%
  ggplot(aes(x= age)) +
  geom_histogram() +
  theme_bw() +
  ggtitle("Age distribution")

unique(d4$comments)
```

### Task time

As a sanity check look at total task time: Expect participants to take longer in the SPSS experiments since its sequential. The data look consistent with this.
```{r, fig.height = 5}
d1 = read.csv("../../exp1/analysis/exp1_A.csv" ) %>%
      mutate(exp = "XT2007a replication (E1)")
d2 = read.csv("../../exp2/analysis/exp2_A.csv" ) %>%
      mutate(exp = "SPSS replication (E2)")
d3 = read.csv("../../exp3/analysis/exp3_A.csv" ) %>%
      mutate(exp = "XT2007a replication (E3), blocked/diff labels")
d4 = mutate(d4, exp = "SPSS replication (E4), blocked/diff labels")

all = rbind(d1, d2, d3, d4)

all$SubmitTime = gsub("T|Z","",all$SubmitTime)
all$AcceptTime = gsub("T|Z","",all$AcceptTime)
all$SubmitTime = strptime(all$SubmitTime, "%F%T")
all$AcceptTime = strptime(all$AcceptTime, "%F%T")
all$total_time = as.numeric(all$SubmitTime) - as.numeric(all$AcceptTime)
all$exp = as.factor(all$exp)
all$exp = factor(all$exp,levels(all$exp)[c(3,4,1,2)])

ggplot(all, aes(x = exp, y = total_time/60)) +
    ylab("Task time (min)") +
    geom_boxplot() +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

all %>%
  select(-AcceptTime, -SubmitTime) %>%
  group_by(exp) %>%
  mutate(total_time = total_time/60) %>%
  multi_boot_standard(column = "total_time") %>%
  ggplot(aes(x = exp, y = mean, fill = exp)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, 
                     ymax = ci_upper), 
                 position=position_dodge(width = .9)) +
  ylab("Task time (min)") +
  xlab("Examples") +
  theme_bw() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



